### 2021-09-10 sections/healthcare_application/main.tex
More changes form code review and fix minor typos

The system defined in section \ref{sec:model_overview} can be applied 
to a healthcare scenario with two such queueing systems.
The two queueing systems can be thought of as two Emergency Departments (ED) and 
the Emergency Medical Services (EMS) as a distributor that distributes 
patients to them.
The parameters of the model correspond to the following parameters of the ED and 
the EMS:

@@

The strategies of the two EDs are the range of thresholds that they can choose
from and their utilities is the proportion of individuals whose time in the 
system is within a predetermined target time.
The EMS has to decide how to distribute its patients among the two EDs so that 
the blocking time of ambulances is minimised. 
As defined in \ref{sec:model_overview}, the interaction between the two EDs 
is a Normal form game that is then used to inform the decision of the EMS.
Note that the formulated game here assumes that prior to making a choice the 
EMS knows the strategies that each ED is playing (figure 
\ref{fig:imperfect-info-game}). This corresponds to reacting to experienced delays.

@@

Consider a game with the following parameters:

@@

\textbf{Increasing \(\lambda_2\):}
Figure \ref{fig:ard_lambda_2} shows a similar run of the
algorithm but when the strategies begin to stabilise an increase in the
arrival rate of ambulances occurs (i.e \( \lambda_2 = 10.7 \)).

\begin{figure}[H]
    \includegraphics[width=\textwidth]{imgs/asymmetric_rd_and_PoA/asymmetric_flooding.pdf}
    \caption{The strategies played when running asymmetric replicator dynamics
    along with the compartmentalised price of anarchy of the blocking time at
    each iteration of the learning algorithm. After a number of iterations the 
    arrival rate of ambulance patients is significantly increased to flood the
    system completely \( \lambda_2 = 10.7 \).}
    \label{fig:ard_lambda_2}
\end{figure}

@@

\textbf{Increasing number of servers \( C_1 and C_2 \):}
Figure \ref{fig:ard_num_of_servers} shows a run of asymmetric replicator 
dynamics with a change in the number of servers of the hospitals.
The number of servers are increased from \(C_1 = 3, C_2 = 2\) to 
\(C_1 = 4, C_2 = 3\).

>>>>

The system defined in section \ref{sec:model_overview} can be applied 
to a healthcare scenario with two such queueing systems.
The two queueing systems can be thought of as two Emergency Departments (ED) and 
the Emergency Medical Services (EMS) as a distributor that distributes 
patients to them.

The parameters of the model correspond to the following parameters of the ED and 
the EMS:

@@

The strategies of the two EDs are the range of thresholds that they can choose
from and their utilities is the proportion of individuals whose time in the 
system is within a predetermined target time.
The EMS has to decide how to distribute its patients among the two EDs so that 
the weighted combination of the ambulance blocking time and the percentage of 
lost ambulances is minimised. 
As defined in \ref{sec:model_overview}, the interaction between the two EDs 
is a Normal form game that is then used to inform the decision of the EMS.
Note that the formulated game here assumes that prior to making a choice the 
EMS knows the strategies that each ED is playing (figure 
\ref{fig:imperfect-info-game}). This corresponds to reacting to experienced delays.

@@

Consider a game with two smaller (lower \( N_i, M_i \)) and busier (higher 
\(\lambda_{1_i} \) and \(\lambda_2\)) hospitals with the following set of 
parameters:

@@

\textbf{Increasing \(\lambda_2\):}
Figure \ref{fig:ard_lambda_2} shows a similar run of the
algorithm but when the strategies begin to stabilise an increase in the
arrival rate of ambulances occurs (i.e \( \lambda_2 = 24 \)).

\begin{figure}[H]
    \includegraphics[width=\textwidth]{imgs/asymmetric_rd_and_PoA/asymmetric_flooding.pdf}
    \caption{The strategies played when running asymmetric replicator dynamics
    along with the compartmentalised price of anarchy of the blocking time at
    each iteration of the learning algorithm. After a number of iterations the 
    arrival rate of ambulance patients is significantly increased to flood the
    system completely \( \lambda_2 = 24 \).}
    \label{fig:ard_lambda_2}
\end{figure}

@@

\textbf{Increasing number of servers \( C_1 \) and \( C_2 \):}
Figure \ref{fig:ard_num_of_servers} shows a run of asymmetric replicator 
dynamics with a change in the number of servers of the hospitals.
The number of servers are increased from \(C_1 = 3, C_2 = 2\) to 
\(C_1 = 4, C_2 = 3\).
